% ---- Don't modify from Line no. 2 to 74 ----
\documentclass[12pt]{article}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{epsfig}
\usepackage{amsmath}   
\usepackage{amssymb}
\usepackage{placeins}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{setspace}
\usepackage{multirow}
\usepackage[export]{adjustbox}[2011/08/13]
\usepackage{tabularx}
\usepackage{algcompatible}
\usepackage{caption}
\usepackage{epsf}
\usepackage{epstopdf}
\usepackage{subfigure} 
\usepackage{colortbl}
\usepackage{longtable}
\usepackage{enumerate}
\usepackage{tabularx, booktabs}

\usepackage[table,xcdraw]{xcolor}

\usepackage{tikz}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{soul}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{placeins}
\usepackage{makecell}
\newcounter{qcounter}
\usepackage{tcolorbox}
\usepackage{lscape}
\usepackage{url}
\usepackage{hyperref}
\usepackage{tablefootnote}
\usepackage{url}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\setlength{\parindent}{4em}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.5}

\usepackage[numbers]{natbib}
\bibliographystyle{unsrtnat}

\begin{document}

% ------------ Don't modify anything up to here ---------------

% From here on-wards modify only the relevant fields, such as Title (line no. 76), "Section:", "Course Instructor:", and "Team Members:" field. (Team Members details should be in the format such as, name, reg. no., mobile no. and email id.). Further, "Title:" can be changed as per your selected topic name. In the brief description field you can describe your topic in 250 words. Additionally, in the "Key Feature:" field add your mini-project feature as an item (example is shown). AT the end in the "Reference:" field add the website/paper/article referred for this mini-project as an item.

\begin{center}
    \textbf{\Large{Abstract \\
    (\textcolor{red}{Car Rental System})}}
\end{center}

\noindent 
\textbf{Course Code:} CS110 
\hspace{2in} 
\textbf{Course Title:} Computer Programming \\
\textbf{Semester:} B. Tech 1$^{st}$ Sem 
\hspace{1.6in} 
\textbf{Section:} S3 \\
\textbf{Academic Year:} 2019-20 
\hspace{1.8in} 
\textbf{Course Instructor:} Vaishnavi T \\
\textbf{Team Members:} \\
\textbf{1.} Pratham N, 191MT034, 6363583848, prathamn452001@gmail.com 
\newline
\textbf{2.} Saransh Bhaduka, 191ME252, 8696966881, saranshbhaduka111@gmail.com
\newline
\textbf{3.} Sumanth N Hegde, 191ME284, 7019468097, mnphah@gmail.com
\newline
\textbf{4.} Prasanna Sarkar, 191MT033, 9472839780, sarkarprasanna2u@gmail.com

\vspace{0.25in}

\noindent
\textbf{Brief Description:}
\newline
We have designed a car rental system which lets the users choose any specific car model to rent. It also allows the users to give their feedback and rating based on the his or her experience. 
\newline
\newline
In this car rental system, the user can choose his desired car from a list of car models available. The user can then specify the number of days he will be using it for, and whether he will be needing a driver or not. The program will then calculate the fee which the user will be urged to pay by visiting a website (for obvious reasons website is non-functional). The rented car will then be added to the user profile, which the user can view anytime he wants to do so. The user can also give his own feedback as to how the service can be improved and also can give a star based rating on how his or her experience was. This whole project was developed using C programming language and various concepts and features such as file handling, structures etc. were utilized. This program is easy to operate and will be easily understood by the users.

\noindent
\textbf{Key Features:}
\begin{enumerate}
    \item Login facility (New or existing account)
    \item Listing car models available
    \item Renting cars
    \item Printing invoice based on duration
    \item User Profile Display
    \item Returning the cars
    \item Feedback/rating facility
\end{enumerate}

\noindent
\textbf{References:}
\begin{enumerate}
    \item https://code-projects.org/car-rental-system-in-c-with-source-code/
    \item https://www.geeksforgeeks.org/basics-file-handling-c/
\end{enumerate}


\begin{center}
    \textbf{**** END ****}
\end{center}

\end{document}
